Haploid Selection, Sex Ratio Bias, and Transitions Between Sex-Determination Systems

### 2017-11-24 LaTeX/Turnover.tex
minor change

\textcolor{blue}{is this specific in any way to tight linkage, $r\approx0$? i see most of the plots referred to are tight linkage plots...}

Generally, haploid selection expands the scenarios under which neo-W alleles can spread. 
For example, when selection is sexually-antagonistic in diploids ($s^\female s^\male <0$ and $0<h^\Hermaphrodite<1$) an unlinked neo-W ($R=1/2$) cannot invade unless there is also haploid selection (Figures \ref{fig:SexAntagTighter} and \ref{fig:SexAntagTighterMaleDrive}). 
Secondly, with haploid selection, overdominance ($w_{aa}^\Hermaphrodite<w_{Aa}^\Hermaphrodite$ \& $w_{AA}^\Hermaphrodite<w_{Aa}^\Hermaphrodite$) is not required for neo-W-$a$ haplotypes to spread ($\lambda_{ma}>1$) (Figures \ref{fig:regionMaleDrive}-\ref{fig:regionFemaleGS}). 
Haploid selection and overdominance allow unlinked neo-W alleles to invade even when there is tight linkage between the ancestral SDR and the selected locus (Figure \ref{fig:loose_invades_tight}).
Finally, haploid selection can maintain a polymorphism in the face of directional selection in male and female diploids (ploidally-antagonistic selection). 
When selection is ploidally-antagonistic, neo-W alleles often spread, for at least some values of $R$ (Figure \ref{fig:regionPloidAntag}).

>>>>

With tight linkage, haploid selection generally expands the conditions under which neo-W alleles can spread. 
For example, when selection is sexually-antagonistic in diploids ($s^\female s^\male <0$ and $0<h^\Hermaphrodite<1$) an unlinked neo-W ($R=1/2$) cannot invade unless there is also haploid selection (Figures \ref{fig:SexAntagTighter} and \ref{fig:SexAntagTighterMaleDrive}). 
Secondly, with haploid selection, overdominance ($w_{aa}^\Hermaphrodite<w_{Aa}^\Hermaphrodite$ \& $w_{AA}^\Hermaphrodite<w_{Aa}^\Hermaphrodite$) is not required for neo-W-$a$ haplotypes to spread ($\lambda_{ma}>1$) (Figures \ref{fig:regionMaleDrive}-\ref{fig:regionFemaleGS}). 
Haploid selection and overdominance allow unlinked neo-W alleles to invade even when there is tight linkage between the ancestral SDR and the selected locus (Figure \ref{fig:loose_invades_tight}).
Finally, haploid selection can maintain a polymorphism in the face of directional selection in male and female diploids (ploidally-antagonistic selection). 
When selection is ploidally-antagonistic, neo-W alleles often spread, for at least some values of $R$ (Figure \ref{fig:regionPloidAntag}).
